---
title: "Immunization Dashboard"
author: "Niall Mannion"
date: "`r format(Sys.time(), '%d %b %Y')`"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
runtime: shiny
resource_files:
- timeseries.csv
---

```{r global, include=FALSE}
# Tang, D. (2018) 'Visualising Google Trends results with R'. Computational biology and genomics Blog. Available
#  https://davetang.org/muse/2018/12/31/visualising-google-trends-results-with-r/``{r global, include=FALSE}

install.packages("textdata", repos="http://cran.r-project.org")
install.packages("gtrendsR", repos="http://cran.r-project.org")
install.packages("ggplot2", repos="http://cran.r-project.org")
install.packages("plotly", repos="http://cran.r-project.org")
install.packages("maps", repos="http://cran.r-project.org")
install.packages("tidytext", repos="http://cran.r-project.org")
install.packages("flexdashboard", repos="http://cran.r-project.org")
library(flexdashboard)
library(textdata)
library(gtrendsR) 
library(ggplot2) 
library(plotly)
library(maps)
library(tidytext)
vaccine_line <- gtrends(c("vaccine", "vaccination", "swine", "covid-19"), geo = "US", time = "all")
plot.gtrends.silent <- function(x, ...) {df <- x$interest_over_time 
  df$date <- as.Date(df$date) 
  df$hits <- if(typeof(df$hits) == 'character'){ 
  as.numeric(gsub('<','',df$hits)) } else { df$hits} 

df$legend <- paste(df$keyword, " (", df$geo, ")", sep = "") 
  p <- ggplot(df, aes_string(x = "date", y = "hits", color = "legend")) + 
    geom_line() + 
    xlab("Date") + 
    ylab("Search hits") + 
    ggtitle("") + 
    theme_bw() + 
    theme(legend.title = element_blank()) 
  invisible(p)} 

my_plot <- plot.gtrends.silent(vaccine_line) 
gt <- my_plot + 
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
  theme(legend.position = "none") 

my_theme <- function() {theme_bw() + theme(panel.background  = element_blank(),
plot.background = element_rect(fill = "seashell"),
panel.border = element_blank(), strip.background  = element_blank(),
plot.margin = unit(c(.5, .5, .5, .5), "cm"),
panel.spacing = unit(3, "lines"), panel.grid.major  = element_blank(),
panel.grid.minor = element_blank(), legend.background = element_blank(),
legend.key = element_blank(), legend.title = element_blank())}
my_theme2 <- function() {my_theme() + theme(axis.title = element_blank(),
axis.text = element_blank(), axis.ticks = element_blank())}
vaccine_gtrends <- gtrends(c("vaccine"), time = "today 12-m", geo = "US") 
vaccine_gtrends <- vaccine_gtrends$interest_by_region
statesMap      <- map_data("state")
vaccine_gtrends$region <- sapply(vaccine_gtrends$location,tolower)
final_gtrends  <- merge(statesMap, vaccine_gtrends,by="region")
regionLabels   <- aggregate(cbind(long, lat) ~ region, data = final_gtrends, 
                  FUN=function(x) mean(range(x)))
g <- final_gtrends %>% ggplot() + geom_polygon(aes(x=long,y=lat,group=group,fill = hits, label = region), colour="white") + scale_fill_continuous(low="ivory",high="midnightblue") +
guides(fill = "colorbar") + my_theme2() + coord_fixed(1.3)

install.packages("dplyr", repos="http://cran.r-project.org")
install.packages("tidyr", repos="http://cran.r-project.org")
install.packages("ggplot2", repos="http://cran.r-project.org")
install.packages("ggrepel", repos="http://cran.r-project.org")
install.packages("gridExtra", repos="http://cran.r-project.org")
install.packages("knitr", repos="http://cran.r-project.org")
install.packages("radarchart", repos="http://cran.r-project.org")
install.packages("wordcloud2", repos="http://cran.r-project.org")
install.packages("twitteR", repos="http://cran.r-project.org")
install.packages("rtweet", repos="http://cran.r-project.org")
library(dplyr)
library(tidyr)
library(ggplot2) 
library(ggrepel)
library(gridExtra) 
library(knitr) 
library(radarchart) 
library(wordcloud2)
library(twitteR)
library(rtweet)

Ninth <- read.csv("09th Mar Texas.csv", header=T, na.strings = c(""), stringsAsFactors = T)
Sixteenth <- read.csv("16th Mar Texas.csv", header=T, na.strings = c(""), stringsAsFactors = T)
TwentyThird <- read.csv("23th Mar Texas.csv", header=T, na.strings = c(""), stringsAsFactors = T)
Thirtieth <- read.csv("30th Mar Texas.csv", header=T, na.strings = c(""), stringsAsFactors = T)

march_tweets <- rbind(Ninth, Sixteenth, TwentyThird, Thirtieth)
march_tweets <- march_tweets[!duplicated(march_tweets$text),]
comb <- march_tweets[ ,c(3, 13, 14, 17, 32, 91, 5)]
Texas_Tweets <- comb
texasdf <- Texas_Tweets %>% dplyr::select(Date = created_at, Text = text, Number_of_Retweets = retweet_count,
                              Language = lang, Location = place)
selected <- c("Date", "Text", "Location")
texasdf[selected] <- lapply(texasdf[selected], as.character)

# function to remove special characters
removeSpecialChars <- function(x) gsub("[^a-zA-Z0-9 ]", " ", x)
# remove special characters
texasdf$Text <- sapply(texasdf$Text, removeSpecialChars)

# convert everything to lower case
texasdf$Text <- sapply(texasdf$Text, tolower)

#define some colors to use throughout
my_colors <- c("#E69F00", "#56B4E9", "#009E73", "#CC79A7", "#D55E00")

theme_lyrics <- function() 
{theme(plot.title = element_text(hjust = 0.5),
       axis.text.x = element_blank(), 
       axis.ticks = element_blank(),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       legend.position = "none")}

final_tweets_filtered <- texasdf %>%
  unnest_tokens(word, Text) %>%
  anti_join(stop_words) %>%
  distinct() %>%
  dplyr::filter(nchar(word) > 3)
undesirable_words <- c("https", "vaccine", "time", "vaccine",
                       "news", "vaccinated", "vaccines",
                       "vaccination", "doesn", "months", "anti",
                       "stop", "ready", "world", "people")

final_tweet_filtered <- texasdf %>%
  unnest_tokens(word, Text) %>%
  anti_join(stop_words) %>%
  dplyr::distinct() %>%
  dplyr::filter(!word %in% undesirable_words) %>%
  dplyr::filter(nchar(word) > 3)

p <- final_tweet_filtered %>%
  dplyr::count(word, sort = TRUE) %>%
  top_n(15) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot() +
  geom_col(aes(word, n), fill = my_colors[4]) +
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5),
        panel.grid.major = element_blank()) +
  xlab("Word") + 
  ylab("Word Count") +
  ggtitle("") +
  coord_flip()
q <- p + theme(axis.text=element_text(size=10),
          axis.title=element_text(size=10))
me <- q 

install.packages("ggrepel", repos="http://cran.r-project.org")
install.packages("syuzhet", repos="http://cran.r-project.org")
library(ggrepel)
library(syuzhet)
texas_nrc <- final_tweet_filtered %>%
  inner_join(get_sentiments("nrc"))

syuzhet_vector <- get_sentiment(final_tweet_filtered$word, method="nrc")
nrc_plot <- texas_nrc %>%
  group_by(sentiment) %>%
  dplyr::summarise(word_count = n()) %>%
  ungroup() %>%
  mutate(sentiment = reorder(sentiment, word_count)) %>%
  ggplot(aes(sentiment, word_count, fill = -word_count)) +
  geom_col() +
  guides(fill = FALSE) + 
  theme_lyrics() +
  labs(x = "Emotion", y = "Word Count") +
  scale_y_continuous(limits = c(0, 25000)) +
  coord_flip()
nrc_plot <- nrc_plot + theme(axis.text=element_text(size=10),
               axis.title=element_text(size=10))
d <- nrc_plot + theme(plot.title = element_text(size=10, face="bold"))

install.packages("plyr", repos="http://cran.r-project.org")
install.packages("ggplot2", repos="http://cran.r-project.org")
library(ggplot2)
library(plyr)
imbalanceddata <- read.csv("NIS_dataset.csv", header=T, na.strings = c(""), stringsAsFactors = T)
imbalanceddata$Duration <- as.numeric(imbalanceddata$Duration) 
imbalanceddata<-na.omit(imbalanceddata) 
imbalanceddata <- imbalanceddata[ ,c(3:19)]

imbalanceddata <- imbalanceddata[!grepl("REFUSED|NEVER HEARD OF WIC|DON'T KNOW", imbalanceddata$WIC),]
imbalanceddata <- imbalanceddata[!grepl("OTHER ARRANGMENT|REFUSED|DON'T KNOW", 
imbalanceddata$House_Ownership_Status),]
imbalanceddata <- imbalanceddata[!grepl("DON'T KNOW|REFUSED", imbalanceddata$Was_Child_Breastfed),]
imbalanceddata <- imbalanceddata[!grepl("NA|TYPE OF PROVIDER UNKNOWN|REFUSED",
imbalanceddata$Provider_Facility),]

imbalanceddata$Was_Child_Breastfed <- factor(imbalanceddata$Was_Child_Breastfed) 
imbalanceddata$Child_Number <- factor(imbalanceddata$Child_Number) 
imbalanceddata$WIC <- factor(imbalanceddata$WIC) 
imbalanceddata$Education_Status <- factor(imbalanceddata$Education_Status) 
imbalanceddata$Mother_Age_Group <- factor(imbalanceddata$Mother_Age_Group) 
imbalanceddata$Marital_Status <- factor(imbalanceddata$Marital_Status) 
imbalanceddata$House_Ownership_Status <- factor(imbalanceddata$House_Ownership_Status) 
imbalanceddata$Race <- factor(imbalanceddata$Race) 
imbalanceddata$Provider_Facility <- factor(imbalanceddata$Provider_Facility) 
imbalanceddata$Insurance_Type <- factor(imbalanceddata$Insurance_Type) 
imbalanceddata$Number_Providers <- factor(imbalanceddata$Number_Providers) 

my_theme <- theme( 
  axis.title.x = element_text(size = 12), 
  axis.text.x = element_text(size = 12), 
  axis.title.y = element_text(size = 12), 
  axis.text.y = element_text(size = 12), 
  plot.title = element_text(size = 12, hjust = 0.5)) 
LT = dim(imbalanceddata)[1]

install.packages("Hmisc", repos="http://cran.r-project.org")
library(Hmisc)

imbalanceddata$Income_Level <- cut(imbalanceddata$Income_Group, 3,  
include.lowest=TRUE, labels=c("Low", "Medium", "High"))
imbalanceddata$Insurance_Type <- revalue(imbalanceddata$Insurance_Type, c("ANY MEDICAID"="Medicaid", "OTHER INSURANCE"="Other", "PRIVATE INSURANCE ONLY" = "Private", "UNINSURED"="Uninsured", "OTHER INSURANCE (CHIP, IHS, MILITARY, OR OTHER, ALONE OR IN COMB. WITH PRIVATE INSURANCE)"="Public")) 
imbalanceddata$Insurance_Type <- factor(imbalanceddata$Insurance_Type, levels=c("Private", "Public", "Medicaid", "Other", "Uninsured"))
imbalanceddata$Race <- revalue(imbalanceddata$Race, c("HISPANIC" = "Hispanic", "NON-HISPANIC OTHER + MULTIPLE RACE" = "Mixed", "NON-HISPANIC BLACK ONLY" = "Black", "NON-HISPANIC WHITE ONLY" = "White"))  
imbalanceddata$Race <- factor(imbalanceddata$Race, 
levels=c("Hispanic", "White", "Mixed", "Black"))
imbalanceddata$Race <- revalue(imbalanceddata$Race, c("HISPANIC" = "Hispanic", "NON-HISPANIC OTHER + MULTIPLE RACE" = "Mixed", "NON-HISPANIC BLACK ONLY" = "Black", "NON-HISPANIC WHITE ONLY" = "White"))  
imbalanceddata$Child_Number <- factor(imbalanceddata$Child_Number, 
levels=c("ONE", "TWO OR THREE", "FOUR OR MORE"))  
imbalanceddata$Child_Number <- revalue(imbalanceddata$Child_Number,   
c("ONE"= "1", "TWO OR THREE" = "2 or 3", "FOUR OR MORE" = ">=4")) 

plot16 <-ggplot(data = imbalanceddata[1:LT,], aes(x = Income_Level,fill = Vaccination_Status)) +  
  geom_bar(position="fill") + ylab("count") + theme(legend.position="left") +
  theme(legend.title = element_text(color = "black", size = 12),
  legend.text = element_text(color = "blue", size = 10)) +
  scale_fill_discrete(name = "Vaccination Status", labels = c("Unvaccinated", "Vaccinated"))
plot10 <-ggplot(data = imbalanceddata[1:LT,], aes(x = Insurance_Type,fill = Vaccination_Status)) +  
  geom_bar(position="fill") + ylab("Count") + theme(legend.title = element_text(color = "black", size = 12),
  legend.text = element_text(color = "blue", size = 10)) +
  scale_fill_discrete(name = "Vaccination Status", labels = c("Unvaccinated", "Vaccinated"))
plot15 <-ggplot(data = imbalanceddata[1:LT,], aes(x = Race, fill = Vaccination_Status)) +  
  geom_bar(position="fill") + ylab("count") + theme(legend.title = element_text(color = "black", size = 12),
  legend.text = element_text(color = "blue", size = 10)) +
  scale_fill_discrete(name = "Vaccination Status", labels = c("Unvaccinated", "Vaccinated"))
plot3 <-ggplot(data = imbalanceddata[1:LT,], aes(x = Child_Number,fill = Vaccination_Status)) +  
  geom_bar(position="fill") + theme(legend.title = element_text(color = "black", size = 12),
  legend.text = element_text(color = "blue", size = 10)) +
  scale_fill_discrete(name = "Vaccination Status", labels = c("Unvaccinated", "Vaccinated")) 
plot1 <-ggplot(data = imbalanceddata[1:LT,], aes(x = Household_Size,fill = Vaccination_Status)) +  
  geom_bar(position="fill") + theme(legend.title = element_text(color = "black", size = 12),
  legend.text = element_text(color = "blue", size = 10)) +
  scale_fill_discrete(name = "Vaccination Status", labels = c("Unvaccinated", "Vaccinated"))
plot5 <-ggplot(data = imbalanceddata, aes(x = Education_Status,fill = Vaccination_Status)) +  
  geom_bar(position="fill") + theme(legend.title = element_text(color = "black", size = 12),
  legend.text = element_text(color = "blue", size = 10)) +
  scale_fill_discrete(name = "Vaccination Status", labels = c("Unvaccinated", "Vaccinated"))
imbalanceddata$Provider_Facility <- revalue(imbalanceddata$Provider_Facility, 
                                            c("ALL HOSPITAL FACILITIES" = "All", "ALL MILITARY/OTHER FACILITIES" =
                                                "Military", "ALL PRIVATE FACILITIES" = "Private", 
                                              "ALL PUBLIC FACILITIES" = "Public", "MIXED"="Mixed"))
imbalanceddata$Provider_Facility <- factor(imbalanceddata$Provider_Facility, 
                                           levels=c("Private", "Public", "Medicaid", "Other", "Uninsured"))
plot11 <-ggplot(data = imbalanceddata[1:LT,], aes(x = Number_Providers,
                                                  fill = Vaccination_Status)) + geom_bar(position="fill") + ylab("Frequency")
plot12 <-ggplot(data = imbalanceddata[1:LT,], aes(x = House_Ownership_Status,
            fill = Vaccination_Status)) + geom_bar(position="fill") + ylab("Frequency") +
            theme(legend.position = "none")
plot13 <-ggplot(data = imbalanceddata[1:LT,], aes(x = Provider_Facility,
                                                  fill = Vaccination_Status)) + geom_bar(position="fill") + ylab("Frequency") +
  theme(legend.position = "none")
plot14 <-ggplot(data = imbalanceddata[1:LT,], aes(x = Mother_Age_Group,
                                                  fill = Vaccination_Status)) + geom_bar(position="fill") + ylab("") 
imbalanceddata$Marital_Status <- revalue(imbalanceddata$Marital_Status, 
     c("MARRIED"="Married", 
     "NEVER MARRIED/WIDOWED/DIVORCED/SEPARATED/DECEASED/LIVING WITH PARTNER" = "Not Currently Married"))
plot8 <- ggplot(data = imbalanceddata[1:LT,], aes(x = Marital_Status,fill = Vaccination_Status)) +
  geom_bar(position="fill") + theme(legend.position = "none")

trains <- read.csv("training_data.csv", header=T, na.strings = c(""), stringsAsFactors = T)
test <- read.csv("test_data.csv", header=T, na.strings = c(""), stringsAsFactors = T)
levels(trains$Vaccination_Status) <- c("Vaccinated", "Unvaccinated")

install.packages("dplyr", repos="http://cran.r-project.org")
install.packages("randomForest", repos="http://cran.r-project.org")
install.packages("SuperLearner", repos="http://cran.r-project.org")
install.packages("ggplot2", repos="http://cran.r-project.org")
library(randomForest) 
library(dplyr) 
library(ggplot2)
library(SuperLearner)

# Variable Importance
# Random Forest
set.seed(232) 
imp_rf <- randomForest(Vaccination_Status ~ ., data=trains,  importance=TRUE) 
var_imp <- varImpPlot(imp_rf)
var_imp <- as.data.frame(var_imp)
var_imp$varnames <- rownames(var_imp)
rownames(var_imp) <- NULL  

b <- ggplot(var_imp, aes(x=reorder(varnames, MeanDecreaseAccuracy),
                    weight=MeanDecreaseAccuracy, fill=varnames)) + 
  geom_bar() + scale_fill_discrete(name="Variable Group") +
  ylab("Importance") + xlab("Variable") +
  coord_flip() + theme(legend.position = "none") + 
  ggtitle("Random Forest Variable Importance") +
  theme(plot.title = element_text(hjust = 0.5))

# Take a sample from the test as a mock datatable. Doctors can use this to view  
# predicted values for their real patient data that they wish to predict 
value <- c(72.7, 17.8 , 87.09, 54.67, 58.97, 53.53, 64.55, 40.86, 70.78, 68.22, 38.37, 76.04, 68.59, 26.24, 79.68, 64.01, 43.06, 69.5, 62.59, 46.62, 66.77, 76.12, 30.01, 80, 59.47, 55.29, 60.56, 71.66, 19.62, 85.3) 
Models <- c(rep("Random Forest" , 3) , rep("Bagging" , 3) , rep("Boosting" , 3) , rep("C-Forest" , 3), 
            rep("KNN" , 3) , rep("Neural Network" , 3) , rep("SVM" , 3) , rep("SuperLearner" , 3), 
            rep("Naive Bayes" , 3) , rep("C5.0" , 3)) 
Measure <- rep(c("Accuracy" , "Sensitivity" , "Specificity") , 10) 
data <- data.frame(Measure, Models, value) 
data 
f <- ggplot(data, aes(fill = Measure, y = value, x = Models)) +  
  geom_bar(position="dodge", stat="identity") + coord_flip()

y <- as.numeric(trains[,14])-1  
ytest <- as.numeric(test[,14])-1  
x <- trains[ ,c(1:13, 15, 16, 17)]  
sl_model <- SuperLearner(y,  
                        x,  
                        SL.library=list("SL.ranger"))

install.packages("DT", repos="http://cran.r-project.org")
library(DT)
test_datatable <- sample_n(test, 1000)
predictions <- predict.SuperLearner(sl_model, test_datatable)  
conv.preds <- ifelse(predictions$pred>=0.5, 1, 0)  
conv.preds <- as.factor(conv.preds) 
library(plyr) 
Predicted_Vaccination_Status <- revalue(conv.preds, c("0"="Unvaccinated", "1"="Vaccinated")) 
bound <- cbind(Predicted_Vaccination_Status, test_datatable)

install.packages("reshape2", repos="http://cran.r-project.org")
install.packages("ggplot2", repos="http://cran.r-project.org")
install.packages("forecast", repos="http://cran.r-project.org")
install.packages("tsoutliers", repos="http://cran.r-project.org")
install.packages("tidyr", repos="http://cran.r-project.org")
install.packages("plotly", repos="http://cran.r-project.org")
install.packages("MTS", repos="http://cran.r-project.org")
install.packages("vars", repos="http://cran.r-project.org")
install.packages("DT", repos="http://cran.r-project.org")
library(reshape2)
library(ggplot2)
library(forecast)
library(tsoutliers)
library(tidyr)
library(plotly)
library(MTS)
library(vars)
library(DT)

headers = read.csv('datatable_timeseries.csv', skip = 1, header = F, nrows = 1, as.is = T)
timeseries = read.csv('datatable_timeseries.csv', skip = 2, header = F)
colnames(timeseries)= headers
timeseries
names(timeseries)[names(timeseries) == "variable"] <- "State"

Arkansas <- c(55.1, 62.1,	74.8,	65.9,	69.5,	66.5,	68.1,	71,	76.5,	82.4,	67.8,	74.9,	75,	78,	38.5,	59.4,	70.5,	70,	60.5,	70.3,	69.7,	72.1,	72.1)
Texas <- c(52.4,	61.8,	65.6,	63.9,	64.5,	62,	70,	67.9,	74.8,	72.5,	78.4,	76.7,	78.2,	78.6,	43.7,	62.8,	74.9,	67.7,	74.6,	67.6,	74,	73.1,	72.3)
Oklahoma <- c(42.8,	58.9,	66,	70.9,	70.5,	68.4,	70.3,	65.3,	70.5,	72.1,	75.7,	80.4,	80.1,	73.6,	60.1,	55.3,	71,	65,	69.4,	76.7,	78.8,	70.9,	71.4)
newsa <- cbind(Texas, Arkansas, Oklahoma)

# analysing timeseries
# new <- filter(tsdf, Names == "Texas"| Names == "Oklahoma"| Names == "Arkansas")
mymts = ts(newsa, frequency = 1, start = c(1995, 1))
newsat <- newsa[ ,c(1)]
Treated = ts(newsat, frequency = 1, start = c(1995, 1))
outliers_excess_ts <- tso(Treated, types = c("TC", "AO", "LS", "IO", "SLS"))
outliers_excess_ts$outliers
(outliers_idx <- outliers_excess_ts$outliers$ind)
n <- length(Treated)
mo_tc <- outliers("TC", outliers_idx)
tc <- outliers.effects(mo_tc, n)
coefhat <- as.numeric(outliers_excess_ts$outliers["coefhat"])
tc_effect <- coefhat*tc
Outlier_Plot <- ts(tc_effect, frequency = frequency(Treated), start = start(Treated))
Untreated <- Treated - Outlier_Plot
Texas <- Untreated

newsat <- newsa[ ,c(2)]
Treated = ts(newsat, frequency = 1, start = c(1995, 1))
outliers_excess_ts <- tso(Treated, types = c("TC", "AO", "LS", "IO", "SLS"))
outliers_excess_ts$outliers
(outliers_idx <- outliers_excess_ts$outliers$ind)
n <- length(Treated)
mo_tc <- outliers("TC", outliers_idx)
tc <- outliers.effects(mo_tc, n)
coefhat <- as.numeric(outliers_excess_ts$outliers["coefhat"])
tc_effect <- coefhat*tc
Outlier_Plot <- ts(tc_effect, frequency = frequency(Treated), start = start(Treated))
Untreated <- Treated - Outlier_Plot
Arkansas <- Untreated

newsat <- newsa[ ,c(3)]
Treated = ts(newsat, frequency = 1, start = c(1995, 1))
outliers_excess_ts <- tso(Treated, types = c("TC", "AO", "LS", "IO", "SLS"))
outliers_excess_ts
outliers_excess_ts$outliers
(outliers_idx <- outliers_excess_ts$outliers$ind)
n <- length(Treated)
mo_tc <- outliers("TC", outliers_idx)
tc <- outliers.effects(mo_tc, n)
coefhat <- as.numeric(outliers_excess_ts$outliers["coefhat"])
tc_effect <- coefhat*tc
Outlier_Plot <- ts(tc_effect, frequency = frequency(Treated), start = start(Treated))
Untreated <- Treated - Outlier_Plot
Oklahoma <- Untreated
adjusted_ts <- cbind(Oklahoma, Texas, Arkansas)


stnry = diffM(adjusted_ts) 
VARselect(stnry, type = "none", lag.max = 10)
var.a <- vars::VAR(stnry, lag.max = 10, ic = "AIC", type = "none") 
fcast = predict(var.a, n.ahead = 5)
par(mar = c(2.5,2.5,2.5,2.5))
plot(fcast)

Texas_fcast = fcast$fcst[2] 
Texas_fcast
x = Texas_fcast$Texas[,1]
tail(adjusted_ts)
x = cumsum(x) + 74.1
par(mar = c(2.5,2.5,1,2.5))
Texas_Forecast =ts(c(adjusted_ts[,2], x), start = c(1995,1), frequency = 1)
Texas_df <- as.data.frame(Texas_Forecast[1:28]) 
colnames(Texas_df) <- c("x")

Arkansas_fcast = fcast$fcst[3] 
Arkansas_fcast
y = Arkansas_fcast$Arkansas[,1]
tail(adjusted_ts)
y = cumsum(y) + 73.89
par(mar = c(2.5,2.5,1,2.5))
Arkansas_Forecast =ts(c(adjusted_ts[,3], y), start = c(1995,1), frequency = 1)
Arkansas_df <- as.data.frame(Arkansas_Forecast[1:28]) 
colnames(Arkansas_df) <- c("y")

Oklahoma_fcast = fcast$fcst[1] 
Oklahoma_fcast
z = Oklahoma_fcast$Oklahoma[,1]
tail(adjusted_ts)
z = cumsum(z) + 71.4
par(mar = c(2.5,2.5,1,2.5))
Oklahoma_Forecast =ts(c(adjusted_ts[,1], z), start = c(1995,1), frequency = 1)
Oklahoma_df <- as.data.frame(Oklahoma_Forecast[1:28]) 
colnames(Oklahoma_df) <- c("z")

combined_ts <- cbind(Texas_Forecast, Arkansas_Forecast, Oklahoma_Forecast)
combined_ts
combined_df <- as.data.frame(combined_ts)
combined_df$Year <- seq(1995, 2022, by = 1)
reshaped_ts <- melt(combined_df, id="Year")
q <- ggplot(data = reshaped_ts, aes(x = Year, y = value, colour = variable)) + geom_line()
q <- ggplotly(q)
```

Online Dashboard {data-icon="fa-comment-o"}
====================

Row{data-height=450}
--------

### Most Common Words In Vaccine Related Texas Tweets
```{r, echo=FALSE}
ggplotly(me)
```

### Most Common Emotions in Vaccine Related Texas Tweets
```{r, echo=FALSE}
ggplotly(d)
```

Row{data-height=500}
--------

### Google Search Hits in 'Vaccine' By State

```{r, echo=FALSE}
ggplotly(g)

```

### Google Search Interest in Vaccine Related Keywords Over Time (US)
```{r, echo=FALSE}
ggplotly(gt)
```

NIS Data Mining {data-icon="fa-database"}
====================
Row
------------------------------------------------------------------------------
### Variable Importance
```{r, echo=FALSE}
ggplotly(b)
```

### Model Performance
```{r, echo=FALSE}
ggplotly(f)
```

Row {.tabset}
---------- 
### Education Status
```{r, echo=FALSE}
ggplotly(plot5)
```

### Household Size
```{r, echo=FALSE}
ggplotly(plot1)
```

### Income Group
```{r, echo=FALSE}
ggplotly(plot16)
```

### Insurance Type
```{r, echo=FALSE}
ggplotly(plot10)
```

### Mother Age Group
```{r, echo=FALSE}
ggplotly(plot14)
```

### Race
```{r, echo=FALSE}
ggplotly(plot15)
```

### Number of Healthcare Providers
```{r, echo=FALSE}
ggplotly(plot11)
```

### Parents' Marital Status
```{r, echo=FALSE}
ggplotly(plot8)
```

Predicted Vaccination Status {data-icon="fa-syringe"}
====================

Row
-------- 
### Table of Predicted Vaccination Status 

```{r, echo=FALSE} 
datatable(bound)
``` 


Time Series Forecasting {data-icon="fa-clock"}
====================
Row
-------- 

### Table of Timeseries Data 
```{r, echo=FALSE} 
datatable(timeseries) 
``` 

Row
---------- 

### Timeseries Forecast Line Chart of Vaccination Rates 

```{r, echo=FALSE} 
ggplotly(q)
```